Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-04-24 ThesisJP/Background/background.tex
Corrected thank-you section.

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{img/cpu_vs_gpu.pdf}
\caption{Development in theoretical peak throughput, single precision (SP) and double precision (DP), the last decade for Intel CPUs and Nvidia GPUs.}
\label{fig:cpu_vs_gpu}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{img/cpu_vs_gpu.pdf}
\caption{Development in theoretical peak throughput, single precision (SP) and double precision (DP), the last decade for Intel CPUs and Nvidia GPUs (github.com/mgalloy/cpu-vs-gpu).}
\label{fig:cpu_vs_gpu}
\end{figure}

### 2014-04-24 ThesisJP/Thesis.tex
Fixed figure layout. Checked all labels.
Some minor corrections.
Corrected thank-you section.

\subsubsection{Acknowledgments}
First of all I would like to thank my main supervisor Sverre Holm and the rest of my team of supervisors for all help and guidance through the Ph.D project. Andreas Austeng also deserves big thank you. In the second part of my Ph.D. project you have been my supervisor more than anyone. Thank you to all my co-authors for their contributions. I also want to thank the Faculty of Medicine, MI-Lab and the Department of Circulation and Medical Imaging, NTNU for believing in me and making it possible to conduct this work.

@@

Thank you to Ines Hafizovic and Carl-Inge Colombo Nilsen for extensive help with reviewing this thesis.

I would like to thank my family and all my friends for all support. But most of all, I want to thank Beate for all her love, patient and support. Without it I would never have manage to complete this theses.
\null
\vfill
\hfill To: Sofie Mathilde \AA{}sen
\CustChapter*{List of publications}
\addcontentsline{toc}{chapter}{List of publications}

@@

>>>>

\subsubsection{Acknowledgments}
First of all I would like to thank my main supervisor Sverre Holm and the rest of my team of supervisors for all the help and guidance through the Ph.D. project. Andreas Austeng also deserves a big thank you for all valuable help and for showing so much interest in my work. Thank you to all my co-authors for their contributions. I also want to thank the Faculty of Medicine, MI-Lab and the Department of Circulation and Medical Imaging, NTNU for believing in me and making it possible to conduct this work.

@@

Ines Hafizovic and Carl-Inge Colombo Nilsen have used their spare time to review this thesis, for which I am very grateful.

Finally I would like to thank my family and all my friends for their support, and for providing a world away from work. But most of all, I want to thank Beate for her love and patient. Without your support I would never have managed to complete this thesis.
\null
\vfill
\hfill Dedicated to Sofie Mathilde \AA{}sen
\CustChapter*{List of publications}
\addcontentsline{toc}{chapter}{List of publications}

@@

\setcounter{chapter}{1}
